Reputational Risk and Questionable Research Practices in Archaeological Science

### 2023-10-06 docs/paper.qmd
caliper tests

>>>>

## Caliper test

```{r}
jasr_caliper <- 
  jasr_exact_zoom_plot_data %>% 
  mutate(in_caliper = ifelse(p_value %in% c(0.03875, 0.04000), 
                             "smaller", 
                             ifelse(p_value %in% c(0.04875, 0.05000), 
                                    "larger", ""))) %>% 
  filter(in_caliper != "") %>% 
  count(in_caliper)

jasr_caliper_test_binom_test <- 
binom.test(jasr_caliper$n[2],
           sum(jasr_caliper$n), 
           p = 1/2,
           alternative = "less")

jasr_caliper_n <- unname(jasr_caliper_test_binom_test$parameter)
jasr_caliper_k <- unname(jasr_caliper_test_binom_test$statistic)
jasr_caliper_p <- round(unname(jasr_caliper_test_binom_test$p.value), 10)

jasr_df <- data.frame(
  x = 0.05,
  y = 140,
  label = paste0(  "N = ", jasr_caliper_n, 
                   ", K = ", jasr_caliper_k, 
                   ", p = ", knitr:::format_sci(signif(jasr_caliper_p, 4), 'html')  , "") 
)

jas_caliper <- 
  jas_exact_zoom_plot_data %>% 
  mutate(in_caliper = ifelse(p_value %in% c(0.03875, 0.04000), 
                             "smaller", 
                             ifelse(p_value %in% c(0.04875, 0.05000), 
                                    "larger", ""))) %>% 
  filter(in_caliper != "") %>% 
  count(in_caliper)

jas_caliper_test_binom_test <- 
binom.test(jas_caliper$n[2],
           sum(jas_caliper$n), 
           p = 1/2,
           alternative = "less")

jas_caliper_n <- unname(jas_caliper_test_binom_test$parameter)
jas_caliper_k <- unname(jas_caliper_test_binom_test$statistic)
jas_caliper_p <- round(unname(jas_caliper_test_binom_test$p.value), 10)

jas_df <- data.frame(
  x = 0.05,
  y = 140,
  label = paste0(  "N = ", jas_caliper_n, 
                   ", K = ", jas_caliper_k, 
                   ", p = ", knitr:::format_sci(signif(jas_caliper_p, 4), 'html')  , "") 
)

```{r}
library(ggtext)

ggplot(jasr_exact_zoom_plot_data) +
  aes(p_value) +
  geom_histogram(bins = 27)  +
  geom_segment(x = 0.05,
            xend = 0.05,
            y = 0,
            yend = 120,
             colour = "red",
            aesthetic = 2) +
  xlim(0.03, 0.07) +
  ylim(0, 150) +
  theme_minimal() +
  ylab("frequency in JASR") +
  xlab("p-value (exactly reported in the article text)") +
  geom_richtext(
    data = jasr_df,
    aes(x, y, 
        label = label),
    fill = NA, 
    label.color = NA,
    size = 10
  ) +
  theme_light(base_size = 18)

ggsave(here::here("figures/jasr_p_value_caliper_test.png"),
       w = 14,
       h = 6,
       dpi = 600)

library(ggtext)

ggplot(jas_exact_zoom_plot_data) +
  aes(p_value) +
  geom_histogram(bins = 27)  +
  geom_segment(x = 0.05,
            xend = 0.05,
            y = 0,
            yend = 120,
             colour = "red",
            aesthetic = 2) +
  xlim(0.03, 0.07) +
  ylim(0, 150) +
  theme_minimal() +
  ylab("frequency in JAS") +
  xlab("p-value (exactly reported in the article text)") +
  geom_richtext(
    data = jas_df,
    aes(x, y, 
        label = label),
    fill = NA, 
    label.color = NA,
    size = 10
  ) +
  theme_light(base_size = 18)

ggsave(here::here("figures/jas_p_value_caliper_test.png"),
       w = 14,
       h = 6,
       dpi = 600)
```
